The Driving Forces of API Evolution

### 2015-06-03 thesis/paper.tex
APIs as Systems
Drafted first two sections of this subsubsection

\subsubsection{APIs as Systems}
1. Clear up how "complex" API is. Explain error handling, 3rd party libs.
2. Explain that our study strictly includes the interface and middle-layer parts (don't refer to it as middle-layer)
3. Also explain that the documentation (SDK) and example code were studied
4. We consider these "artefacts" as the system of our study
...transition...
1. Defnition of system
2. Relate to previously made points
...transition...
1. Refer back to background (e-type)
2. Make the case for why our API is an e-program

>>>>

\subsubsection{APIs as Systems}
% 1. Clear up how "complex" API is. Explain error handling, 3rd party libs.
% 2. Explain that our study strictly includes the interface and middle-layer parts (don't refer to it as middle-layer)
% 3. Also explain that the documentation (SDK) and example code were studied
% 4. We consider these "artefacts" as the system of our study
% ...transition...
The case company's API is a complex API. When studying the API, we have focused on the interfaces and the intersecting layer of the API. (!!! expand?). Given that the implementation of the API is usually hidden and irrelevant from the users perspective, we will not be inspecting it for changes. We are also inspecting the entire SDK which was made available to us by company A. The SDK includes artefacts such as the API documentation, user manuals and other miscellaneous documentation. We therefore believe that the use of third party libraries, error handling, daemons and an extensive interconnected API, combined with an extensive SDK, indicates to us that this API can be considered as a system.
% 1. Definition of system
% 2. Relate to previously made points
% ...transition...
The IEEE defines a system to be ``A combination of interacting elements organised to achieve one or more stated purposes...Organised to accomplish a specific function or set of functions within a specific environment". The combination of the interacting parts of the API, coupled with the specific nature of the problem the API is addressing and the fact that this API is developed for embedded systems, allows us to argue that this definition accurately supports our intent to classify this API as a system.

% 1. Refer back to background (e-type)
% 2. Make the case for why our API is an e-program
